rcitoid
=========

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.com/ropenscilabs/rcitoid.svg?branch=master)](https://travis-ci.com/ropenscilabs/rcitoid)
[![Build status](https://ci.appveyor.com/api/projects/status/yk8vpcdr1rmi7byy?svg=true)](https://ci.appveyor.com/project/sckott/rcitoid)
[![codecov](https://codecov.io/gh/ropensci/rcitoid/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/rcitoid)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/rcitoid)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/rcitoid)](https://cran.r-project.org/package=rcitoid)


```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL,
            x[lines],
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

rcitoid

Client for the Citoid service <https://www.mediawiki.org/wiki/Citoid>

docs: <https://en.wikipedia.org/api/rest_v1/#!/Citation/getCitation>

## Install

Development version

```{r eval=FALSE}
devtools::install_github("ropenscilabs/rcitoid")
```

Load the package


```{r}
library("rcitoid")
```

## get citation data

DOI

```{r output.lines=1:10}
cit_oid("10.1108/jd-12-2013-0166")
```

PMID

```{r output.lines=1:10}
cit_oid(30446726)
```

PMCID

```{r output.lines=1:10}
cit_oid("PMC4679344")
```

ISBN

```{r output.lines=1:10}
cit_oid(1439895619)
```

## Meta

* Please [report any issues or bugs](https://github.com/ropenscilabs/rcitoid/issues)
* License: MIT
* Get citation information for `rcitoid` in R doing `citation(package = 'rcitoid')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
